On The Efficiency of Jet Production in Radio Galaxies

### 2015-10-19 paper.tex
Nova subsecao paper.tex
Henrique changed the latex file
Added a subsection and changed the following subsection.

\subsection{New subsection}
% Measuring jet efficiencies: why? importance
% inspired on bullet points of slide #7 from talk to Ramesh's group, Nov. 2013
One promising approach for probing the physical conditions behind jet launching in AGNs is to evaluate the energy efficiency of jet production which we define as $\eta_{\rm jet} \equiv P_{\rm jet}/(\dot{M}_{\rm BH} c^2)$, given appropriate measurements of the jet power $P_{\rm jet}$ \emph{and} the mass accretion rate onto the black hole $\dot{M}_{\rm BH}$. Estimating the efficiency of jet production gives us an indirect diagnostic of the jet formation process and the source of jet power. For instance, high efficiencies would suggest spin powering and possibly dynamically important magnetic fields near the horizon (e.g., \citealt{Sasha11,Zamaninasab14}) as opposed to an outflow from an accretion disk \citep{Blandford82,Ghosh97,Livio99}. $\eta_{\rm jet}$ is also relevant for our understanding of the ``radio mode'' of AGN feedback in massive early-type galaxies (e.g., \citealt{Allen06,McNamara07,Fabian12}) and it impacts the cosmological evolution and growth of massive black holes (e.g., \citealt{Fanidakis11,Volonteri12}).

@@

Eu agradeco ao meu pai e a minha mae. Um beijo no coracao de todo o mundo. Git eh muito util. etc etc
We acknowledge useful discussions with Mihoko Yukita, Ka-Wah Wong, Aleksander Sadowski, Helen Russell, Jonathan C.~McKinney, Jeremy Schnittman, Markos Georganopoulos, Ramesh Narayan, Jeff McClintock, Feng Yuan and Sylvain Guiriec (who the f&&k are these people????). RSN was partially supported by the NASA Postdoctoral Program (NPP) at Goddard Space Flight Center, administered by Oak Ridge Associated Universities through a contract with NASA, as well as the NASA grant NNH10ZDA001N and FAPESP. AT was supported by by NASA through Einstein Postdoctoral Fellowship grant number PF3-140115 awarded by the Chandra X-ray Center, which is operated by the Smithsonian Astrophysical Observatory for NASA under contract NAS8-03060, and NASA support via High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center that provided access to the Pleiades supercomputer, as well as NSF support through an XSEDE computational time allocation TG-AST100040 on NICS Kraken, Nautilus, TACC Stampede, Maverick, and Ranch. This project made considerable use of IPython \citep{ipython} and the Astropy and mcerp libraries.

>>>>

% Measuring jet efficiencies: why? importance
% inspired on bullet points of slide #7 from talk to Ramesh's group, Nov. 2013
One promising approach for probing the physical conditions behind jet launching in AGNs is to evaluate the energy efficiency of jet production which we define as $\eta_{\rm jet} \equiv P_{\rm jet}/(\dot{M}_{\rm BH} c^2)$, given appropriate measurements of the jet power $P_{\rm jet}$ \emph{and} the mass accretion rate onto the black hole $\dot{M}_{\rm BH}$. Estimating the efficiency of jet production gives us an indirect diagnostic of the jet formation process and the source of jet power. For instance, high efficiencies would suggest spin powering and possibly dynamically important magnetic fields near the horizon (e.g., \citealt{Sasha11,Zamaninasab14}) as opposed to an outflow from an accretion disk \citep{Blandford82,Ghosh97,Livio99}. $\eta_{\rm jet}$ is also relevant for our understanding of the ``radio mode'' of AGN feedback in massive early-type galaxies (e.g., \citealt{Allen06,McNamara07,Fabian12}) and it impacts the cosmological evolution and growth of massive black holes (e.g., \citealt{Fanidakis11,Volonteri12}).

@@

We acknowledge useful discussions with Mihoko Yukita, Ka-Wah Wong, Aleksander Sadowski, Helen Russell, Jonathan C.~McKinney, Jeremy Schnittman, Markos Georganopoulos, Ramesh Narayan, Jeff McClintock, Feng Yuan and Sylvain Guiriec. RSN was partially supported by the NASA Postdoctoral Program (NPP) at Goddard Space Flight Center, administered by Oak Ridge Associated Universities through a contract with NASA, as well as the NASA grant NNH10ZDA001N and FAPESP. AT was supported by by NASA through Einstein Postdoctoral Fellowship grant number PF3-140115 awarded by the Chandra X-ray Center, which is operated by the Smithsonian Astrophysical Observatory for NASA under contract NAS8-03060, and NASA support via High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center that provided access to the Pleiades supercomputer, as well as NSF support through an XSEDE computational time allocation TG-AST100040 on NICS Kraken, Nautilus, TACC Stampede, Maverick, and Ranch. This project made considerable use of IPython \citep{ipython} and the Astropy and mcerp libraries.
